Meta-analysis of the Interoceptive Accuracy Scale

### 2025-07-06 analysis/study2.qmd
updated manuscript
update

library(tidyverse)
library(easystats)
library(patchwork)
library(lavaan)
library(ggraph)
library(tidySEM)
library(EGAnet)
```

@@

vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
# vars_intero <- vars_cfa[vars_cfa != "CoughSneeze"]

@@

## Empirical Scores vs. Model-based

vars_scores <- names(select(scores$sample1a, -Sample))
df_scores <- rbind(
  select(df1a, all_of(vars_scores)),
  select(df1b, all_of(vars_scores)),
  select(df2, all_of(vars_scores)),
  select(df3, all_of(vars_scores)),
  select(df4, all_of(vars_scores)),
  select(df5, all_of(vars_scores)),
  select(df6, all_of(vars_scores)),
  select(df7a, all_of(vars_scores)),
  select(df7b, all_of(vars_scores)),
  select(df7c, all_of(vars_scores)),
  select(df8a, all_of(vars_scores)),
  select(df8b, all_of(vars_scores)),
  select(df9, all_of(vars_scores)),
  select(df10a, all_of(vars_scores)),
  select(df10b, all_of(vars_scores)),
  select(df10c, all_of(vars_scores)),
  select(df11a, all_of(vars_scores)),
  select(df11b, all_of(vars_scores))
)

order <- c("WindBurp", "CoughSneeze", "MusclesPain", "ItchBruise", "HeartBreathing", "HungryThirsty", "UrinateDefecate")

correlation::correlation(select(df_scores, -all_of(vars_intero)),
                         select(df_scores, all_of(vars_intero))) |> 
  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
    mutate(Parameter2 = fct_relevel(Parameter2, rev(order)),
           Parameter1 = fct_relevel(Parameter1, paste0("CFA_", order), "EGA3", "EGA2", "EGA4", "EGA1")) |>
    ggplot(aes(x = Parameter1, y = Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_gradient(low="blue", high="red", limit = c(0.1, 1), guide = guide_colourbar(ticks = FALSE)) +
    theme_minimal() +
    theme(
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

Even EGA components capture pairs or groupings of pairs of items.

@@

```{r}
make_diff <- function(df, vars, component=NA) {
  df <- select(df, all_of(c("Gender", "Sample", vars)))
  df <- df[complete.cases(df), ]
  dat <- data.frame()
  for (resp in vars) {
    f <- as.formula(paste0(resp, "~ Gender"))
    d <- filter(df, Gender %in% c("Male", "Female")) |>
      mutate(Gender = fct_relevel(Gender, "Male", "Female"))
    dat <- effectsize::cohens_d(f, data=d) |>
      as.data.frame() |>
      mutate(var_Correlate = "Gender", 
             var_Interoception = resp,
             p=t.test(f, data=d)$p.val) |>
      rbind(dat)
  }

  dat$r <- effectsize::d_to_r(dat$Cohens_d, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
  dat$CI_low <- effectsize::d_to_r(dat$CI_low, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
  dat$CI_high <- effectsize::d_to_r(dat$CI_high, n1=sum(df$Gender=="Male"), n2=sum(df$Gender=="Female"))
  dat$Sample <- unique(df$Sample)
  dat$Component <- component
  select(dat, -Cohens_d)
}

data <- rbind(
  make_diff(df1a, vars_intero, component="Demographic"),
  make_diff(df1b, vars_intero, component="Demographic"),
  make_diff(df2, vars_intero, component="Demographic"),
  make_diff(df3, vars_intero, component="Demographic"),
  #make_diff(df4, vars_intero, component="Demographic"),
  #make_diff(df5_attention, vars_intero, component="Demographic"),
  make_diff(df6, vars_intero, component="Demographic"),
  make_diff(df7a, vars_intero, component="Demographic"),
  make_diff(df7b, vars_intero, component="Demographic"),
  make_diff(df7c, vars_intero, component="Demographic"),
  make_diff(df8a, vars_intero, component="Demographic"),
  make_diff(df8b, vars_intero, component="Demographic"),
  make_diff(df9, vars_intero, component="Demographic"),
  make_diff(df10a, vars_intero, component="Demographic"),
  make_diff(df10b, vars_intero, component="Demographic"),
  make_diff(df10c, vars_intero, component="Demographic"),
  make_diff(df11a, vars_intero, component="Demographic"),
  make_diff(df11b, vars_intero, component="Demographic")
) |>
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

@@

```{r}
make_cor <- function(df, vars, with = "Age", component=NA) {
  df <- select(df, all_of(c(with, "Sample", vars)))
  df <- df[complete.cases(df), ]

  dat <- data.frame()
  for (v in vars) {
    dat <- correlation::cor_test(df, v, with) |>
      rename(var_Interoception = Parameter1, var_Correlate = Parameter2) |>
      as.data.frame() |>
      rbind(dat)
  }

  dat$Sample <- unique(df$Sample)
  dat$Component <- component
  select(dat, -df_error, -t, -Method, -n_Obs)
}

data <- rbind(
  data,
  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df11a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df11b, vars_intero, with = "Age", component="Demographic")
)
```

@@

```{r}
names(df2)[str_detect(names(df2), "MAIA")]  
names(df4)[str_detect(names(df4), "MAIA")]  # individual items
names(df7a)[str_detect(names(df7a), "MAIA")]  
names(df7b)[str_detect(names(df7b), "maia")] 
names(df7c)[str_detect(names(df7c), "MAIA")]
names(df10a)[str_detect(names(df10a), "MAIA")]
names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
names(df10c)[str_detect(names(df10c), "MAIA")]
names(df11a)[str_detect(names(df11b), "MAIA")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),
  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),

  # df4

  # df7a
  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df7b
  make_cor(df7b, vars_intero, with = "maiaNotice", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7b, vars_intero, with = "maiaNonDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7b, vars_intero, with = "maiaNotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7b, vars_intero, with = "maiaAttentionRegulation", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7b, vars_intero, with = "maiaEmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7b, vars_intero, with = "maiaSelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7b, vars_intero, with = "maiaBodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7b, vars_intero, with = "maiaTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df7c
   make_cor(df7c, vars_intero, with = "MAIA_noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7c, vars_intero, with = "MAIA_notdis", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7c, vars_intero, with = "MAIA_notwor", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7c, vars_intero, with = "MAIA_attreg", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7c, vars_intero, with = "MAIA_emoaw", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7c, vars_intero, with = "MAIA_selfreg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7c, vars_intero, with = "MAIA_bodlis", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7c, vars_intero, with = "MAIA_trust", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df10a
  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  #df10b

  # df10c 
  make_cor(df10c, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10c, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10c, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10c, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10c, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10c, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10c, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10c, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

    # df11a
  make_cor(df11a, vars_intero, with = "MAIA_Attention", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df11a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df11a, vars_intero, with = "MAIA_Emotional", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df11a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df11a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df11a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df11a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df11a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting")
)
```

@@

names(df2)[str_detect(names(df2), "ICQ")] 
names(df7c)[str_detect(names(df7c), "ICQ")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "ICQ", component="ICQ") |>
    mutate(var_Correlate = "ICQ"),
  make_cor(df7c, vars_intero, with = "ICQ_sum", component="ICQ") |>
    mutate(var_Correlate = "ICQ")
)

@@

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
names(df3)[str_detect(names(df3), "BPQ")]  
names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items

@@

```{r}
#  only one study assess alexithymia with BVAQ (df2)
names(df2)[str_detect(names(df2), "TAS")]
names(df3)[str_starts(names(df3), "TAS")]
names(df7c)[str_starts(names(df7c), "TAS")]
names(df8b)[str_starts(names(df8b), "TAS")]
names(df11a)[str_starts(names(df11a), "TAS")]

@@

```{r}
names(df6)[str_detect(names(df6), "PHQ")] 
names(df7b)[str_detect(names(df7b), "PHQ")]
names(df7c)[str_detect(names(df7c), "BDI")]
names(df8b)[str_detect(names(df8b), "PHQ")]
names(df9)
names(df11a)

@@

```{r}
names(df6)[str_detect(names(df6), "GAD")] 
names(df7a)[str_detect(names(df7a), "STAI")] 
names(df7b)[str_detect(names(df7b), "STAI")] 
names(df7c)[str_detect(names(df7c), "STAI")]
names(df10b)[str_detect(names(df10b), "STAI")] 
names(df11a)[str_detect(names(df11a), "ANX")] # anx = stai-t

@@

```{r}
names(df7a)[str_detect(names(df7a), "NEO")]
names(df9)[str_detect(names(df9), "BFI_")]
names(df10a)[str_detect(names(df10a), "IPIP6_")]

@@

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
    mutate(var_Correlate = "Alive"),
  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
    mutate(var_Correlate = "Changing"),
  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
    mutate(var_Correlate = "Enticing"),
  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
    mutate(var_Correlate = "Good"),
  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
    mutate(var_Correlate = "Hierarchical"),
  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
    mutate(var_Correlate = "Safe"),
  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
    mutate(var_Correlate = "Understandable"),
  make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
    mutate(var_Correlate = "Alive"),
  make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
    mutate(var_Correlate = "Changing"),
  make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
    mutate(var_Correlate = "Enticing"),
  make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
    mutate(var_Correlate = "Good"),
  make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
    mutate(var_Correlate = "Hierarchical"),
  make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
    mutate(var_Correlate = "Safe"),
  make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
    mutate(var_Correlate = "Understandable")
)
```

@@

## Internal Reliability

- sample df7c does not have individual BPQ items

# BPQ 46 Items SV
df2_BPQ <- df2 |> select(contains("BPQ ")) 
df3_BPQ <- df3 |> select(contains("BPQ"), -contains("BPQ_"))

# BPQ 26 items - awareness subscale

df4_BPQ_A <- df4 |> select(contains("BPQ_"))

# BPQ 12 items VSF
df7a_BPQVSF <- df7b |> select(contains("BPQ_"), -BPQ_Sum)
df8a_BPQVSF <- df8a |> select(contains("BPQ"), -BPQ_A)

@@

average_corr <- data |>
    summarise(mean_r = mean(r, na.rm = TRUE), .by=c("Component", "var_Correlate", "var_Interoception"))

average_corr |>
  filter(Component == "Alexithymia") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "BPQ") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "MAIA") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "ICQ") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Mood") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Maladaptive") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Schizotypic") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Autistic") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Personality") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "World Beliefs") |>
  # group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

>>>>

library(tidyverse)
library(easystats)
library(patchwork)
```

@@

vars_intero <- names(select(scores$sample1a, -Sample))

@@

@@

pool_coef <- function(with = "Age", component = "Demographic", standardize="within") {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in list(df1a, df1b, df2, df3, df4, 
                     df5, df6, df7a, df7b, df7c, 
                     df8a, df8b, df9, df10a, df10b, 
                     df10c, df11a, df11b)) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        if(standardize == "within") d <- standardize(d)
        data <- rbind(data, d)
      }
    }

    if(standardize == "between") {
      data <- standardize(data[complete.cases(data), ])
    }

    if (with == "Gender") {
      data <- data[data$Gender != "Other",]
      data$Gender <- factor(data$Gender, levels = c("Male", "Female"))
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
    } else {
      f <- as.formula(paste0(with, "~", intero, " + (", intero, "|Sample)"))
      f2 <- as.formula(paste0(with, "~", intero, " + (1|Sample)"))
    }

    # if(length(unique(data$Sample)) == 1)
    m <- glmmTMB::glmmTMB(f, data = data)
    type <- "Full"
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f2, data = data)
      type <- "Reduced"
    }
    out <- parameters::parameters(m)[2, ] |> 
      select(r = Coefficient, CI_low, CI_high, p) |> 
      as.data.frame()
    out$var_Interoception <- intero
    out$var_Correlate <- with
    out$Component <- component
    out$Method <- standardize
    out$Type <- type
    out$Converged <- insight::is_converged(m)
    rez <- rbind(rez, out)

  }
  rez
}

make_rez <- function(with = "Gender", component = "Demographic", name = with) {
  d <- rbind(
    pool_coef(with = with, component = component, standardize="within"),
    pool_coef(with = with, component = component, standardize="between")) 
  d$var_Correlate <- name
  d
}

data <- make_rez(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
```

@@

data <- rbind(data, make_rez(with = "Age", component = "Demographic"))
```

@@

```{r}
# names(df2)[str_detect(names(df2), "MAIA")]  
# names(df4)[str_detect(names(df4), "MAIA")]  # individual items
# names(df7a)[str_detect(names(df7a), "MAIA")]  
# names(df7b)[str_detect(names(df7b), "maia")] 
# names(df7c)[str_detect(names(df7c), "MAIA")]
# names(df10a)[str_detect(names(df10a), "MAIA")]
# names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
# names(df10c)[str_detect(names(df10c), "MAIA")]
# names(df11a)[str_detect(names(df11b), "MAIA")]

# data <- rbind(
#   data,
#   make_rez(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation"),
#   make_rez(with = "MAIA_BodyListening", component = "MAIA", name = "Listening"),
#   make_rez(with = "MAIA_BodyTrusting", component = "MAIA", name = "Trusting"),
#   make_rez(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness"),
#   make_rez(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting"),
#   make_rez(with = "MAIA_Noticing", component = "MAIA", name = "Noticing"),
#   make_rez(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying"),
#   make_rez(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation"),
#   make_rez(with = "MAIA_Trusting", component = "MAIA", name = "Trusting")
# )

@@

```{r}
# names(df2)[str_detect(names(df2), "ICQ")] 
# names(df7c)[str_detect(names(df7c), "ICQ")]

data <- rbind(data, make_rez(with = "ICQ", component="ICQ", name = "ICQ"))
```

@@

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
# names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
# names(df3)[str_detect(names(df3), "BPQ")]  
# names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
# names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
# names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items

@@

```{r}
#  only one study assess alexithymia with BVAQ (df2)
# names(df2)[str_detect(names(df2), "TAS")]
# names(df3)[str_starts(names(df3), "TAS")]
# names(df7c)[str_starts(names(df7c), "TAS")]
# names(df8b)[str_starts(names(df8b), "TAS")]
# names(df11a)[str_starts(names(df11a), "TAS")]

@@

```{r}
# names(df6)[str_detect(names(df6), "PHQ")] 
# names(df7b)[str_detect(names(df7b), "PHQ")]
# names(df7c)[str_detect(names(df7c), "BDI")]
# names(df8b)[str_detect(names(df8b), "PHQ")]
# names(df9)
# names(df11a)

@@

```{r}
# names(df6)[str_detect(names(df6), "GAD")] 
# names(df7a)[str_detect(names(df7a), "STAI")] 
# names(df7b)[str_detect(names(df7b), "STAI")] 
# names(df7c)[str_detect(names(df7c), "STAI")]
# names(df10b)[str_detect(names(df10b), "STAI")] 
# names(df11a)[str_detect(names(df11a), "ANX")] # anx = stai-t

@@

```{r}
# names(df7a)[str_detect(names(df7a), "NEO")]
# names(df9)[str_detect(names(df9), "BFI_")]
# names(df10a)[str_detect(names(df10a), "IPIP6_")]

@@

data <- rbind(data, make_rez(with = "PI_Alive", component="World Beliefs", name = "Alive"))

# data <- rbind(
#   data,
#   make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
#     mutate(var_Correlate = "Alive"),
#   make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
#     mutate(var_Correlate = "Changing"),
#   make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
#     mutate(var_Correlate = "Enticing"),
#   make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
#     mutate(var_Correlate = "Good"),
#   make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
#     mutate(var_Correlate = "Hierarchical"),
#   make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
#     mutate(var_Correlate = "Safe"),
#   make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
#     mutate(var_Correlate = "Understandable"),
#   make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
#     mutate(var_Correlate = "Alive"),
#   make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
#     mutate(var_Correlate = "Changing"),
#   make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
#     mutate(var_Correlate = "Enticing"),
#   make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
#     mutate(var_Correlate = "Good"),
#   make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
#     mutate(var_Correlate = "Hierarchical"),
#   make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
#     mutate(var_Correlate = "Safe"),
#   make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
#     mutate(var_Correlate = "Understandable")
# )
```

@@

@@

average_corr <- data |>
  summarise(min_r = min(r, na.rm = TRUE), 
            mean_r = mean(r, na.rm = TRUE),
            max_r = max(r, na.rm = TRUE), 
            Max = var_Interoception[which.max(abs(r))],
            .by=c("Component", "var_Correlate"))

sort(table(average_corr$Max), decreasing = TRUE)

average_corr |> 
  gt::gt() |> 
  gt::data_color(
    columns = c(mean_r, min_r, max_r),
    palette = c("#2196F3", "white", "#FF5722"),
    domain = c(-0.7, 0, 0.7)
  ) |>
  gt::data_color(
    columns = c(Component, Max)
  ) |> 
  gt::fmt_auto()
```
